Designing Machine Learning Pipeline Toolkit for AutoML Surrogate Modeling Optimization

### 2023-06-14 paper/paper.tex
paper edits for doi entries
Signed-off-by: ppalmes <ppalmes@gmail.com>

\usepackage{amsfonts}       % blackboard math symbols
%\usepackage{nicefrac}       % compact symbols for 1/2, etc.
%\usepackage{microtype}      % microtypography
%\usepackage[usecolors=true]{jlcode}    % julia code
\usepackage{graphicx}
%\usepackage{subfigure}
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{float}
\usepackage{listings}
\lstset
{
    language=Julia,
    numbers=left,
    stepnumber=1,
    breaklines=true,
    linewidth=\columnwidth
}
\newfloat{lstfloat}{htbp}{lop}
\floatname{lstfloat}{Listing}
\def\lstfloatautorefname{Listing}
\usepackage{hyperref}
\newcommand{\theHalgorithm}{\arabic{algorithm}}

@@

It is with this background that AMLP was developed. It started as a hobby to
learn \emph{Julia} by implementing ML algorithms.
Due to it's high performance, \emph{Julia} provides a great
playground to test ideas and gain results easily,
which then triggers the desire to test more ideas, all achievable in a short amount of time.
The resulting explorations can easily be turned into a package which is highly
readable but at the same time highly efficient and fast.  The open-source
AMLP is the product of such good usability in Julia. By open sourcing
AMLP, we want to pass on the benefits we received from the machine
learning, open-source, and \emph{Julia} communities. We are hoping
that AMLP can serve as a ML playground to those who want to
study the application of ML workflow and easily extend and benchmark their
creations. The future goal is to help users of AMLP and the \emph{Julia} community
in general to transition from being consumers to becoming producers of ML ideas
and share their creations with future generations and hopefully feed them back to AMLP
or other similar toolkits.

>>>>

\usepackage{amsfonts}       % blackboard math symbols
%\usepackage{nicefrac}       % compact symbols for 1/2, etc.
%\usepackage{microtype}      % microtypography
%\usepackage[usecolors=true]{jlcode}    % julia code
\usepackage{graphicx}
%\usepackage{subfigure}
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{float}
\usepackage{listings}
\lstset
{
    language=Julia,
    numbers=left,
    stepnumber=1,
    breaklines=true,
    linewidth=\columnwidth
}
\newfloat{lstfloat}{htbp}{lop}
\floatname{lstfloat}{Listing}
\def\lstfloatautorefname{Listing}
\usepackage{hyperref}
\newcommand{\theHalgorithm}{\arabic{algorithm}}
\usepackage{doi}
\usepackage{hyperref}

@@

It is with this background that AMLP was developed. It started as a hobby to
learn \emph{Julia} by implementing ML algorithms.
Due to its high performance, \emph{Julia} provides a great
playground to test ideas and gain results easily,
which then triggers the desire to test more ideas, all achievable in a short amount of time.
The resulting explorations can easily be turned into a package which is highly
readable but at the same time highly efficient and fast.  The open-source
AMLP is the product of such good usability in Julia. By open sourcing
AMLP, we want to pass on the benefits we received from the machine
learning, open-source, and \emph{Julia} communities. We are hoping
that AMLP can serve as a ML playground to those who want to
study the application of ML workflow and easily extend and benchmark their
creations. The future goal is to help users of AMLP and the \emph{Julia} community
in general to transition from being consumers to becoming producers of ML ideas
and share their creations with future generations and hopefully feed them back to AMLP
or other similar toolkits.
